Model

### 2020-06-24 prototype/explanatory text.Rmd
added a seperate "model" explanation -- currently incomplete, needs likelihood function; simplified "about" text.
edits to "model" text (replace "d" with "b"); edits to explanatory text (changed depiction of prior)

This application estimates how likely an attorney used peremptory challenges during jury selection to strike potential jurors based on their race or gender. The analysis builds on prior work by @Kadane2018 and @Barrett2007 on statistical analysis for _Batson_ challenges.

To estimate such bias, this application relies on (1) user-inputted data on how an attorney has used strikes in the case before them; and (2) if available, jury-selection data on that attorney's use of strikes in some past cases during 2013-2017 in the federal district court for the District of Connecticut.

@@

The dashed lines indicate a pre-set _credible interval_, i.e., here the values of $d$ between which 80% of the likely values of $b$ fall. If zero falls within this interval, then we should be wary about (have low confidence in) inferring bias (for or against the cognizable class) from the strike data alone. If zero falls outside this interval, we should feel confident in inferring bias from that strike data.

@@

### References

>>>>

This application estimates how likely an attorney used peremptory challenges during jury selection to strike potential jurors based on their race or gender. The analysis builds on prior work on statistical analysis for _Batson_ challenges. To estimate such bias, this application relies on (1) user-inputted data on how an attorney has used strikes in the case before them; and (2) if available, jury-selection data on that attorney's use of strikes in some past cases during 2013-2017 in the federal district court for the District of Connecticut.

@@

The dashed lines indicate a pre-set _credible interval_, i.e., here the values of $b$ between which 80% of the likely values of $b$ fall. If zero falls within this interval, then we should be wary about (have low confidence in) inferring bias (for or against the cognizable class) from the strike data alone. If zero falls outside this interval, we should feel confident in inferring bias from that strike data.

@@

### 2020-06-24 prototype/model_text.Rmd
edits to "model" text (replace "d" with "b"); edits to explanatory text (changed depiction of prior)

Like @Kadane2018 and @Barrett2007, we model the probability that the struck person belonged (or not) to the cognitive class as a function of (1) the number of cognizable class members (e.g., racial minorities, women) and non-class members (e.g., White people, men) in the set of people who could have been struck; and (2) an unobserved variable $b$ that indicates how much weight the striking party placed on the struck juror's membership in the cognitive class (e.g., whether that juror was racial minority or White; women or man).

@@

We are interested in estimating the likely values of $b$, given the strike data we have. There is zero bias only if the probability of striking a cognizable class member is the same as the probability of striking a non-cognitive class member.  Accordingly,

$$w = \frac{Pr(X=1)}{Pr(X = 0)}$$
$$w = e^b$$
$$b \sim \text{Normal}(0, 2)$$

This way, if it is equally likely that a member and non-member of the cognizable class will be stricken, then $w = \frac{Pr(X=1)=0.50}{Pr(X = 0)=0.50}=1$. If so, our measure of bias is zero: given $w=e^b$, then $e^b=1$ and $b=log(1)=0$. If $b>1$, we infer that the the party has bias favoring a strike against a juror falling within the cognitive class ($X=1$, e.g., the juror is a racial minority). Where $b<1$, the party has bias toward striking a juror falling outside the cognitive class ($X=0$, e.g., the juror is White).

@@

The likelihood function of b is 
$$L(b|X) = \prod_{i=1}^{n_i} \prod_{j=1}^{n_j}(\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}})^{\delta_{ij}} (\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}})^{1-\delta_{ij}}$$
where $n_{i}$ is the total number of jury selections and $n_j$ is the total number of peremptory strikes; and where $\delta_{ij} = 1$ when $X_{ij} = 1$ and $\delta_{ij} = 0$ when $X_{ij}=0$.

>>>>

Like @Kadane2018 and @Barrett2007, we model the probability that the struck person belonged (or not) to the cognizable class as a function of (1) the number of cognizable class members (e.g., racial minorities, women) and non-class members (e.g., White people, men) in the set of people who could have been struck; and (2) an unobserved variable $b$ that indicates how much weight the striking party placed on the struck juror's membership in the cognizable class (e.g., whether that juror was racial minority or White; women or man).

@@

We are interested in estimating the likely values of $b$, given the strike data we have. There is zero bias only if the probability of striking a cognizable class member is the same as the probability of striking a non-cognizable class member.  Accordingly,

$$w = \frac{Pr(X=1)}{Pr(X = 0)}$$
$$w = e^b$$
$$b \sim \text{Normal}(\mu_b,\sigma_b)$$
$$\mu_b = 0$$
$$\sigma_b = 2$$

This way, if it is equally likely that a member and non-member of the cognizable class will be stricken, then $w = \frac{Pr(X=1)=0.50}{Pr(X = 0)=0.50}=1$. If so, our measure of bias is zero: given $w=e^b$, then $e^b=1$ and $b=log(1)=0$. If $b>1$, we infer that the the party has bias favoring a strike against a juror falling within the cognizable class ($X=1$, e.g., the juror is a racial minority). Where $b<1$, the party has bias toward striking a juror falling outside the cognizable class ($X=0$, e.g., the juror is White).

@@

The likelihood function of b is 
$$L(b|X) = \prod_{i=1}^{n_i} \prod_{j=1}^{n_j}(\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}})^{\delta_{ij}} (\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}})^{1-\delta_{ij}}$$
where $n_{i}$ is the total number of jury selections; $n_j$ is the total number of peremptory strikes; $\delta_{ij} = 1$ when $X_{ij} = 1$; and $\delta_{ij} = 0$ when $X_{ij}=0$.
